Automated Formal Synthesis of Provably Safe Digital Controllers for Continuous Plants

### 2019-01-31 automatica/paper.tex
+comment

An additional error is due to the representation of the plant dynamics, namely 
%
{\scriptsize
\begin{equation*}
x_{k+1} =\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
\end{equation*}
}
We encompass this error using interval arithmetic~\cite{moore1966interval} in the precision check shown in Figure~\ref{fig:CEGIS-precision-increment} and detailed in the following section.

>>>>

An additional error is due to the representation of the plant dynamics, namely 
%
{\scriptsize
\begin{equation*}
x_{k+1} =\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
\end{equation*}
}
We encompass this error using interval arithmetic~\cite{moore1966interval} in the precision check shown in Figure~\ref{fig:CEGIS-precision-increment} and detailed in the following section \note{previous section?}.
